---
title: "Emily Chu Assignment 7&8"
output: html_notebook
---

# Assignment

Data frame for this assignment:  empdat_cor (download from Canvas)


##### Part I Correlation

**1.	What is the appropriate measure(s) of association/correlation for current salary and education? Why?**
<br>
Pearson's r - we are testing the strength between two variables.

**2.	Generate the appropriate measures(s) of association/correlation for current salary and education. Is the relationship significant? Why?**
```{r}
cor(empdat_cor$salary, empdat_cor$educ, method="pearson", use="complete.obs")
cor.test(empdat_cor$salary, empdat_cor$educ) # give us the p - value, is it significant?
# What does R squared tell us?
CE <- cor(empdat_cor$salary, empdat_cor$educ, method="pearson", use="complete.obs")
CE^2 
```
<br>Yes, the relationship is significant with p-value <2.2e-16. 44% of variation in salary is explained by education and is considered statistically significant.
<br>
**3.	Choose one of the three visualization plots to show the correlation matrix for all the variables in the dataset empdat_cor. Which two variables have the strongest correlation relationship?**

```{r}
library(dplyr)
corrmatrix <- cor(empdat_cor, use="complete.obs")

install.packages('corrplot')
library(corrplot)

corrplot(corrmatrix, method="circle") # corrmatrix is the name of the correlation matrix we created above

corrplot.mixed(corrmatrix, number.cex = 0.8, tl.cex = 0.6)
#number.cex changes the size of the number fonts. tl.cex changes the size of the labels

corrplot(corrmatrix, type="lower")
```


##### Part II Simple Regression

*1.	Generate and interpret a simple regression model for the relationship between current salary and age. Using the ‘sjPlot’ package to show the regression output.*
<br><br>
*a.	Show your regression model output.*
```{r}
regression_1 <- lm(salary ~ age, data = empdat_cor)

#R default regression output:
summary(regression_1)


install.packages("sjPlot")
install.packages("stargazer")
library(sjPlot)
library(stargazer)

sjt.lm(regression_1, 
       show.header = TRUE,
       p.numeric = FALSE,
       show.se = TRUE,
       show.fstat = TRUE, 
       string.est = "Estimate",
       string.ci = "Conf. Int.",
       string.dv = "Unadjusted Regression Model",
       depvar.labels = c("Salary"),
       pred.labels = c("Age"))
```
```
<br><br>

*b.	How much variance in salary can be explained by age?*<br>
With a one year increase in age, salary decreases by $211.61.<br>
About 2.1% variance in salary can be explained by age (unadjusted)
<br><br>

*c.	Is age a significant predictor of salary? How do you know?*<br>
Yes. It is significant at the p<.01 level, which meets the standard p<.05 threshold.
<br><br>

*d.	If someone’s age increased by one year, by how much would you expect their salary to change?*<br>
21%
<br><br>

*e.	Is the model significant? Why?<br>*
Yes, the model is significant because age is a significant predictor of salary.
<br><br>

*f.	Speculate on the nature of the relationship between age and salary in this dataset.<br>*
As age increases, salary increases.

