---
title: "R Notebook"
output: html_notebook
---

### Emily Chu: Assignment 4

Data frame for this assignment:  lowbwt<br><br>
**1.	List the level of measurement for each of the following variables:**

a.	LOW: ordinal-level
b.	AGE: interval-ratio
c.	the new categorical LWT variable that you created in the last assignment: ordinal-level

**2.	Conduct the appropriate hypothesis test to determine if there is a difference in mother's weight in pounds at the last menstrual period between those who had a low birth weight baby and those who did not.**

a.	Use variables at the appropriate level of measurement.
LWT(y): interval-ratio
LOW(x): weight at last menstrual period
b.	Show R syntax.
c.	Show results table.
d.	Report technical results.
e.	Comment on the implications of the result of the test.

```{r}
aggregate(LWT~LOW, lowbwt, mean)
```
```{r}
t.test(LWT~LOW,lowbwt)
```

**Technical Results:** The result is statistically significant for t(132.46)=2.5155 at a p-value of 0.01308 with more low birth weight babies coming from mothers with lower weight at the last menstrual period.

**Implications of Results:** In groups of mothers with a mean weight of around 122 lbs at last menstrual period, you can expect more low birth weight babies than in groups of mothers with a mean weight of around 133 lbs at last menstrual period.

**3.	Conduct the appropriate hypothesis test to determine if there is a difference in the birth weight of the baby between those who smoked during pregnancy and those who did not.**

a.	Use variables at the appropriate level of measurement.
BWT(y): interval-ratio
SMOKE(x): ordinal-level
b.	Show R syntax.
c.	Show results table.
d.	Report technical results.
e.	Comment on the implications of the result of the test.

```{r}
aggregate(BWT~SMOKE, lowbwt, mean)
```
```{r}
t.test(BWT~SMOKE,lowbwt)
```


**Technical Results:** The result is statistically significant for t(170)=2.7095 at a p-value of 0.00743 with babies seeing a lower birth weight in grams from mothers who smoke.

**Implications of Results:** You can expect a significantly lower baby birth weight on average from mothers who smoke than from mothers who don't smoke.

**4.	If you wanted to conduct a two-sample hypothesis test, but both of your variables were interval- ratio, which of the following tasks would you need to complete in order to be able to conduct the test? Select only one answer:**

*b.	Recode the independent variable into a nominal or ordinal variable.*

Submit your work in both HTML file and PDF file (open the HTML file and choose print then save as PDF). 